### 2015-01-19 src/methodology.Rnw
update tables

In order to ensure that the operators that we added were not redundant,
we computed their operator subsumption matrix. This is given in
Table~\ref{tbl:subsumption}, and a visualization of the subsumption is
presented in Figure~\ref{fig:subsumption}. In the figure, the amount of
subsumption is indicated by removal of area from the circle, with same
operators subsuming themselves entirely. This suggests that the operators
we used were non-redundant, with a maximum subsumption of only $40\%$.
The Figure~\ref{fig:mutationshare} shows the share of each mutation operators
in the total number of mutants produced, and the Figure~\ref{fig:mutationkills}
shows the detection and covering rate of mutants by test cases.

>>>>

In order to ensure that the operators that we added were not redundant,
we computed their operator subsumption matrix. This is given in
Table~\ref{tbl:subsumption}. In the table, the mean number of mutants
of an operator in the row subsumed by another operator in the column
is given as the decimal fraction (i.e $1.0$ suggests complete subsumption
of one mutation operator by the other). A visualization of the subsumption is
presented in Figure~\ref{fig:subsumption}. In the figure, the amount of
subsumption is indicated by removal of area from the circle, with same
operators subsuming themselves entirely. This suggests that the operators
we used were non-redundant, with a maximum subsumption of only $40\%$.
The Figure~\ref{fig:mutationshare} shows the share of each mutation operators
in the total number of mutants produced, and the Figure~\ref{fig:mutationkills}
shows the detection and covering rate of mutants by test cases.

### 2015-01-19 src/tbl.pitmut.Rnw
update tables

\begin{table}
\small{
\begin{tabular}{ll}
\hline \hline \\
\Pitin & Remove negative sign from numbers\\
\Pitrv & Mutate return values\\
\Pitm & Mutate arithmetic operators\\
\Pitvmc & Remove void method calls\\
\Pitnc & Negate conditional statements\\
\Pitcb & Modify boundaries in logical conditions\\
\Piti & Modify increment and decrement statements\\
\Pitnvmc & Remove non-void method calls, returning default value \\
\Pitcc & Replace constructor calls, returning null \\
\Pitic & Replace inline constants with default value \\
\Pitri & Remove increment and decrement statements \\
\Pitemv & Replace member variable assignments with default value \\
\Pites & Modify switch statements \\
\Pitrs & Replace switch labels with default (thus removing them) \\
\Pitrc & Replace boolean conditions with true\\
\Pitnc & Replace boolean conditions with false\\
\hline
\end{tabular}
}
\caption{PIT Mutation Operators (We have used abbreviations instead of operator names.)}
\label{tbl:pitop}
\end{table}

>>>>

In order to ensure that the operators that we added were not redundant,
we computed their operator subsumption matrix. This is given in
Table~\ref{tbl:subsumption}. In the table, the mean number of mutants
of an operator in the row subsumed by another operator in the column
is given as the decimal fraction (i.e $1.0$ suggests complete subsumption
of one mutation operator by the other). A visualization of the subsumption is
presented in Figure~\ref{fig:subsumption}. In the figure, the amount of
subsumption is indicated by removal of area from the circle, with same
operators subsuming themselves entirely. This suggests that the operators
we used were non-redundant, with a maximum subsumption of only $40\%$.
The Figure~\ref{fig:mutationshare} shows the share of each mutation operators
in the total number of mutants produced, and the Figure~\ref{fig:mutationkills}
shows the detection and covering rate of mutants by test cases.
